|

### 2023-07-17 paper/05-discussion.Rmd
small edits to rapm paragraph text

Through multilevel modeling, we observe that the pass rusher explains more variation in play-level STRAIN, followed by the possession team, the pass rushing team, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure. However, our model is limited in that we only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects. The nested structure of our model enforces positive dependence between pass rushers on the same team, which may or may not be true. For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. This could leave the path open for another player to rush the quarterback with ease, leading to high STRAIN values. In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach. The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models. We leave this type of analysis for future work, which will require careful consideration of informative prior information [@matano2023augmenting].

>>>>

Through multilevel modeling, we observe that the pass rusher explains more variation in their play-level STRAIN, followed by the possession team, the pass rushing team, and finally the pass rusher's assigned blocker.
This is an intuitive result, consistent with previous literature on pass rushing and pressure. However, our model is limited in that we only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects. The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true. For instance, if one player is known to be an elite pass rusher then the opposing blocking team may focus their blocking efforts on this player. This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values. In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach. The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models. We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].
